---
title: "Joins_Practice"
author: "Julia Parish"
date: "8/17/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(palmerpenguins)
library(lubridate)

```

## **Part 1: Data wrangling refresher**
Refresher 1: Starting with the penguins dataset in the palmerpenguins package, write a single piped sequence in which you:
- Only include penguins at Biscoe and Dream islands
- Remove the year and sex variables
- Add a new column called body_mass_kg, with penguin mass converted from grams to kilograms
- Rename the island variable to location

```{r}
bd_penguins <- penguins %>% 
  filter(island %in% c("Biscoe", "Dream")) %>% 
  select(-year, -sex) %>% 
  mutate(body_mass_kg = body_mass_g / 1000) %>% 
  rename(location = island)
    
```
## **Refresher 2: Staring with the penguins dataset in the palmerpenguins package, write a single piped sequence in which you:**
- Limit to only Adelie penguins
- Remove any observations where flipper_length_mm is NA (hint: !is.na())
- Group the data by sex
- Find the mean (mean()), standard deviation (sd) and sample size (n) of flipper_length_mm for male and female Adelie penguins, returned in a nice summary table

```{r}
ex_2 <- penguins %>% 
  filter(species == "Adelie") %>% 
  drop_na(flipper_length_mm) %>% 
  group_by(sex) %>% 
  summarize(
    mean_flip = mean(flipper_length_mm),
    sd_flip = sd(flipper_length_mm),
    sample_size = n()
  )
```

## Joins Practice
- Datapasta
```{r}
animals <- tibble::tribble(
  ~location,   ~species,  ~maturity,
   "lagoon",   "bobcat",    "adult",
    "bluff",   "coyote", "juvenile",
    "creek",      "fox",    "adult",
     "oaks", "squirrel", "juvenile",
    "bluff",   "bobcat",    "adult"
  )

sites <- tibble::tribble(
           ~location,      ~full_site_name, ~jurisdiction,
             "beach",       "Goleta Beach",     "SB City",
            "lagoon",        "UCSB Lagoon",        "UCSB",
             "bluff",       "Ellwood Mesa",     "SB City",
              "oaks", "Fremont Campground",        "USFS",
           )

```

## Full Join - keeps all data, create new column of data

```{r}
animals_full_join <- full_join(animals, sites)
```

## Left Join - keeps everything in 'x', 

```{r}
animals_left_join <- left_join(animals, sites, by = "location")
```

## Inner join - keeps the things that have a matching key in both x, y

```{r}
animals_inner_join <- inner_join(animals, sites, by = "location")
```

### Filtering Joins
# Semi-joins - keeps all columns in x and keeps observations (rows) where the key has matching values in y

```{r}
animals_semi_join <- semi_join(animals, sites, by = "location")

```

# Anti-join - keeps observations in x if they do not have a matching value in y

```{r}
animals_anti_join <- anti_join(animals, sites, by = "location")

animals_anti_join2 <- anti_join(sites, animals, by = "location")

```

# can join multiple datasets but typically want to do it in steps, and can join together different ways:
*join_pipe <- animals %>% 
  full_join(sites) %>% 
  inner_join(animals_inner_join)*

